To Airbnb?: Factors impacting short-term leasing preference

### 2018-11-28 papers/full_paper_no_authors.Rmd
Revision #3

---
title: "To Airbnb?: Factors impacting short-term leasing preference"
subtitle: "Andy Krause and Gideon Aschwanden"
author: "Zillow and University of Melbourne"
date: "Revised: November 10th, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "To Airbnb?: Factors impacting short-term leasing preference"
# subtitle: "Andy Krause and Gideon Aschwanden"
# author: "Zillow and University of Melbourne"
date: "Revised: November 25th, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---

### 2018-11-28 papers/round_3_reviews.Rmd
Revision #3

---
title: "To Airbnb?: Factors impacting short-term leasing preference"
subtitle: 'Review Update'
date: "11/22/2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
---

@@

#### 1. Bolstered the literature review

@@

#### 2. Added Conditional Expectations Section

>>>>

---
title: "To Airbnb?: Factors impacting short-term leasing preference"
subtitle: 'Review Update'
date: "11/25/2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
---

@@

#### 1. Bolstered the literature review (pgs 2-5)

@@

#### 2. Added Conditional Expectations Section (pgs 24 - 26)
